---
title: "Report title"
subtitle: "Subtitle that indicates findings"
author: "Report prepared for MINGAR by Elden Company"
date: 2022-04-07
lang: "en"
output:
  pdf_document:
    template: report.tex
    toc: true
    toc_depth: 2
titlepage: true
titlepage-color: "428742"
titlepage-text-color: "FFFFFF"
titlepage-rule-color: "FFFFFF"
titlepage-rule-height: 2
---

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(lme4)
library(rvest)
library(polite)
library(lmtest)
library(scales)

# this should suppress all code and messages
knitr::opts_chunk$set(include=FALSE)
```

```{r}
# Q1 
# read in complete customer data
full_cust <- read_rds("data/full_cust.Rds")
# group 'Advance' and 'Active' line together, and rescale income, age
# also, regroup the random effect released_year, due to small number of observations and 
# Active/Advance non-existence before 2019
cust <- full_cust %>% 
  mutate(y = ifelse(line == "Advance" | line == "Active", 1, 0),
         med_inc_10k = median_inc / 10000,
         released_year = format(as.Date(released), "%Y"),
         released_year = ifelse(as.numeric(released_year) > 2019, released_year, "2019 and before"))
# rescale age
cust$age <- 1 - scales::rescale(cust$dob)


# Q2
# read in the complete sleep data
full_sleep <- read_rds("data/full_sleep.Rds")
# refactor line, skin tone, create offset flag for visualizing
sleep <- full_sleep %>% 
  mutate(line = fct_relevel(line, "Run", after = 0),
         skin = fct_relevel(skin, "light", "medium-light", "medium", "medium-dark", "dark", "unknown", after = 0),
         flags_per_h = flags / duration * 60)
# rescale age
sleep$age <- 1 - scales::rescale(sleep$dob)

```

```{r}
# exploratory plots/tables
# Q1
prop.table(table(cust$sex, cust$y), 1)
prop.table(table(cust$released_year, cust$y), 1)

# visualize by-group relation between median income and new product purchase
cust %>% 
  ggplot(aes(x = y, y = median_inc, group=y)) +
  facet_grid(~released_year) +
  geom_boxplot() + 
  theme_minimal()

# Q2
# visualize offset on the number of flags as per 8 hours
sleep %>%
  group_by(skin) %>%
  summarize(mean_count = mean(flags), var_count = var(flags),
            mean_per_h = mean(flags_per_h), var_per_h = var(flags_per_h), n = n(), .groups = "drop")
```

```{r, cache=TRUE}
# Q1 models
mod1 <- lme4::glmer(y ~ age + med_inc_10k + sex + skin +
                      (1 + med_inc_10k + age | released_year), 
                    family = 'binomial', data = cust,
                    control=glmerControl(optimizer="bobyqa",  optCtrl=list(maxfun=2e5)))
summary(mod1)

mod2 <- lme4::glmer(y ~ age + med_inc_10k + sex + skin +
                      (1 + med_inc_10k | released_year), 
                    family = 'binomial', data = cust,
                    control=glmerControl(optimizer="bobyqa",  optCtrl=list(maxfun=2e5)))
summary(mod2)

mod3 <- lme4::glmer(y ~ age + med_inc_10k + sex + skin +
                      (1 + age | released_year), 
                    family = 'binomial', data = cust,
                    control=glmerControl(optimizer="bobyqa",  optCtrl=list(maxfun=2e5)))
summary(mod3)

mod4 <- lme4::glmer(y ~ age + med_inc_10k + sex + skin +
                      (1 | released_year), 
                    family = 'binomial', data = cust,
                    control=glmerControl(optimizer="bobyqa",  optCtrl=list(maxfun=2e5)))
summary(mod4)

mod5 <- lme4::glmer(y ~ age + med_inc_10k +
                      (1 + med_inc_10k| released_year), 
                    family = 'binomial', data = cust,
                    control=glmerControl(optimizer="bobyqa",  optCtrl=list(maxfun=2e5)))
summary(mod5)

mod6 <- lme4::glmer(y ~ med_inc_10k + 
                      (1 + med_inc_10k| released_year),
                    family = 'binomial', data = cust,
                    control=glmerControl(optimizer="bobyqa",  optCtrl=list(maxfun=2e5)))
summary(mod6)

lmtest::lrtest(mod2, mod1) # not different
lmtest::lrtest(mod3, mod1) # different
lmtest::lrtest(mod4, mod2) # different
lmtest::lrtest(mod5, mod2) # not different
lmtest::lrtest(mod6, mod2) # different
# mod5 is the best

lattice::dotplot(lme4::ranef(mod5, condVar=TRUE)) 
```

```{r, cache=TRUE}
# Q2 models, interaction between fix effects not considered
model1 <- glmer(flags ~ skin + sex + age + (1 + skin + age | dev_id), family = poisson,
                offset = log(duration), data = sleep,
                control=glmerControl(optimizer="bobyqa",  optCtrl=list(maxfun=2e5)))
summary(model1)

model2 <- glmer(flags ~ skin + sex + age + (1 + age | dev_id), family = poisson,
                offset = log(duration), data = sleep,
                control=glmerControl(optimizer="bobyqa",  optCtrl=list(maxfun=2e5)))
summary(model2)

model3 <- glmer(flags ~ skin + sex + age + (1 | dev_id), family = poisson,
                offset = log(duration), data = sleep,
                control=glmerControl(optimizer="bobyqa",  optCtrl=list(maxfun=2e5)))
summary(model3) # "best"

model4 <- glmer(flags ~ skin + age + (1 | dev_id), family = poisson,
                offset = log(duration), data = sleep,
                control=glmerControl(optimizer="bobyqa",  optCtrl=list(maxfun=2e5)))
summary(model4)

model5 <- glmer(flags ~ skin + sex + (1 | dev_id), family = poisson,
                offset = log(duration), data = sleep,
                control=glmerControl(optimizer="bobyqa",  optCtrl=list(maxfun=2e5)))
summary(model5)

lmtest::lrtest(model2, model1)
lmtest::lrtest(model3, model1)
lmtest::lrtest(model4, model3)
lmtest::lrtest(model5, model3)

# attempted using line as predictor too, removed random effect
model6 <- glm(flags ~ skin + sex + age + line + skin:age + skin:line + age:skin, family = poisson,
              offset = log(duration), data = sleep)
summary(model6)

model7 <- glm(flags ~ skin + sex + age + line + skin:line, family = poisson,
              offset = log(duration), data = sleep)
summary(model7)

model8 <- glm(flags ~ skin + sex + age + line, family = poisson,
              offset = log(duration), data = sleep)
summary(model8)

model9 <- glm(flags ~ skin + age + line, family = poisson,
              offset = log(duration), data = sleep)
summary(model9) # "best"

model10 <- glm(flags ~ skin + age, family = poisson,
              offset = log(duration), data = sleep)
summary(model10)

anova(model6, model7, model8, model9, model10, test = "Chisq")

```

\newpage
# Executive summary




\newpage
# Technical report

## Introduction

_Provide a brief introduction to your report and outline what the report will cover. This section is valuable for setting scope and expectations. _

### Research questions

This report aimed to answer the following questions with statistical tools:

- How are the buyers of the 'Active' and 'Advance' products different to the buyers of other products? In particular, is the income of customers buying the 'Active' and 'Advance' products different than the buyers of other products?
- Does the skin tone of a customer affect the performance of Mingar wearable devices, particularly in measuring the sleep scores?

## Informative title for section addressing a research question

_For each research question, you will want to briefly describe any data manipulation, show some exploratory plots/summary tables, report on any methods you use (i.e. models you fit) and the conclusions you draw from these_


## Informative title for section addressing a research question

\[\begin{aligned}
Y_{ij} \mid U &\sim Poisson(\mu_{ij}, \theta) \\
\mu_{ij} &= X_{ij}\beta + U_i \\
U &\sim \mathrm{MVN}(0, \Sigma)
\end{aligned}\]



## Discussion

_In this section you will summarize your findings across all the research questions and discuss the strengths and limitations of your work. It doesn't have to be long, but keep in mind that often people will just skim the intro and the discussion of a document like this, so make sure it is useful as a semi-standalone section (doesn't have to be completely standalone like the executive summary)._

### Strengths and limitations

\newpage
# Consultant information
## Consultant profiles

*Complete this section with a brief bio for each member of your group. If you are completing the project individually, you only need to complete one for yourself. In that case, change the title of this section to 'Consultant profile' instead. Examples below. This section is only marked for completeness, clarity and professionalism, not 'truth' so you can write it as if we're a few years in the future. Put your current degree in as completed and/or add your first choice grad school program, whatever you like. What skills related skills would you most like to highlight? What job title do you want?*

**Statsy McStatsstats**. Statsy is a senior consultant with Eminence Analytics. She specializes in data visualization. Statsy earned her Bachelor of Science, Specialist in Statistics Methods and Practice, from the University of Toronto in 2023.

**Datana Scatterplot**. Datana is a junior consultant with Eminence Analytics. They specialize in reproducible analysis and statistical communication. Datana earned their Bachelor of Science, Majoring in Computer Science and Statistics from the University of Toronto in 2024.

## Code of ethical conduct

_This section should be fairly short, no more than half a page. Assume a general audience, much like your executive summary._

* _Make at least three relevant statements about your company's approach to ethical statistical consulting. These should be appropriately in line with professional conduct advice like the (Statistical Society of Canada Code of Conduct)[https://ssc.ca/sites/default/files/data/Members/public/Accreditation/ethics_e.pdf] or the (Ethical Guidelines for Statistical Practice from the American Statistical Society)[https://www.amstat.org/ASA/Your-Career/Ethical-Guidelines-for-Statistical-Practice.aspx]. For example, "the customer is always right" ISN'T the type of thing an ethical statistical consultant would include._
*	_Be very careful not to just copy and paste from these other documents! Put things in your own words._


\newpage
# References

_You don't need to cite course materials, but consider all the the places you got data from, as well as the packages used and R itself. These are all things you should consider citing. Likewise, you might use some external resources on the emoji skin tones/Fitzpatrick scale, etc._

> Douglas Bates, Martin Maechler, Ben Bolker, Steve Walker (2015). Fitting Linear Mixed-Effects Models Using lme4. Journal of Statistical Software, 67(1), 1-48. <https://doi.org/10.18637/jss.v067.i01>.

> R Core Team (2021). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL <https://www.R-project.org/>.

> Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686, <https://doi.org/10.21105/joss.01686>.

\newpage
# Appendix

_These appendices should outline in more detail the steps taken to access the following datasets. They should NOT include code, but should briefly describe the steps and important considerations. I.e., show that you understand what needs to be considered when web scraping, protecting licensed data, etc._

## Web scraping industry data on fitness tracker devices

## Accessing Census data on median household income

## Accessing postcode conversion files


__Final advice: KNIT EARLY AND OFTEN!__
